### 2015-09-28 Paper1.tex
added tex file

\documentclass[a4paper, 11pt]{article}

%===================Packages=====================%
\usepackage[utf8]{inputenc}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{graphicx}
\usepackage{subfig}

\usepackage[pdftex,
pdfauthor={Clemens Fiedler},
pdftitle={Asymmetric Agents and their Willingness to Fight}]{hyperref}

\usepackage[round]{natbib}
\usepackage[nottoc]{tocbibind}

\usepackage{enumerate} %better control over enumerate/itemize
\usepackage{listings}

%\usepackage{tikz}
%\usetikzlibrary{calc}

%\setlength{\parindent}{0pt}

%-------------------------------------------------------------
%Section Naming
%\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
%\renewcommand{\thesubsubsection}{\thesection.\alph{subsection}.\roman{subsubsection}}

%-------------------------------------------------------------
%Graphics
%\usepackage{pgfplots}
%\pgfplotsset{compat=1.9}

%-------------------------------------------------------------
%General Mathematics
\renewcommand{\d}{\text{d}}

%------------------------------------------------------------
%theorem
%\newtheorem{name}{text}
\newtheorem{exmp}{Example}
\newtheorem{assump}{Assumption}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

%-------------------------------------------------------------
%Probability Theory
%\DeclareMathOperator*{\plim}{plim}
\DeclareMathOperator{\sign}{sign}

%-------------------------------------------------------------
%Miscellaneous Packages
%\usepackage{listings} %code in Latex

%-------------------------------------------------------------
% Page Layout
%\usepackage{fullpage} %less margins
\usepackage[margin=2cm]{geometry} %better margin control
% Geometry: margin, left, right

\author{Clemens Fiedler}
\title{Asymmetric Agents and their Willingness to Fight\\
	Customer Loyalty and its Impact on Competition}

\begin{document}

\maketitle

Consider the market for smartphones. Two firms compete over customers with heterogeneous preferences. For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.

Customer $k$ exhibit a preference for one of the two products that is given by $\theta_k$. $\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she has a preference for neither of the firms. Preferences of the customers are distributed according to the cdf $G(\cdot)$ and the pdf $g(\cdot)$.

The preferences are taken as exogenously given. They are either derived from a non-marketable unique characteristic of the products (some people dislike the sharp shape, others love it), or they are derived from previous interactions with the firm. More about this later.

Firms compete in R\&D efforts to increase the quality of their own products. While having a higher quality level helps to gain customers from the competitors, it does not help to increase the return per customer. People are willing to pay a certain amount for a smartphone, but as better products enter the market, the prices for the worse products decrease so that the quality frontier always receives the same valuation.

Customer $k$ purchases product $2$ if and only if the difference in quality overcompensates for her own loyalty:
$$\theta_k\geq x_1-x_2$$

If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue tu purchase its devices. Thus, the demand for firm $1$ is given by:
\begin{align*}
G(x_1-x_2)
\end{align*}

Efforts cause convex costs such that the profits of both firms are given by:
\begin{align}
G(x_1-x_2)\gamma_1 - c_1x_1^2/2\\
\big(1-G(x_1-x_2)\big)\gamma_2 - c_2x_2^2/2
\end{align}

The optimal effort level for both firms is thus:
\begin{align}
x_1^C = g(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\\
x_2^C = g(x_1^C-x_2^C)\frac{\gamma_2}{c_2}
\end{align}
\textbf{Here some things are missing (zero efforts, asymmetry, etc...)}Thus, w.l.g. we can normalize the effort costs to $1$. Depending on the shape of $G(\cdot)$ the game might have multiple equilibria. To avoid uniqueness the following discussion focuses only on local changes.

The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:
\begin{align}
\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\gamma_1\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\gamma_1}{1+g'(x_1^C-x_2^C)\gamma_1}
\end{align}
If $g'(x_1^C-x_2^C)<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.

If $-1<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation. The increase in $x_2$ increases the number of indifferent customers, such that competition becomes more intense. If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.

Returning to the example of the smartphone sector. Consider $g(\cdot)$ such that it is $-1<g'(\theta)$ for all $\theta$. Additionally, most customers are centered in the middle with smaller tails. This can be described by: $g'(0)=0$ and $g'(\theta)<0, \theta>0$,$g'(\theta)<0, \theta<0$. Most customer are willing to switch to the superior product, while a small number has some inherent preference for one.

Now consider a third party, that is maximizing a function of $x_1, x_2$. The utility of the research and development expenses of the firm is given by $U(x_1,x_2)$ with $\frac{\partial U(x_1,x_2)}{\partial x_1},\frac{\partial U(x_1,x_2)}{\partial x_2}>0$. This is achieved my affecting the incentives of the firms. To simplify the problem assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm with $\gamma_1>\gamma_2$. The optimal $\gamma_2$ is given by:

\begin{align}
\frac{\d U(x_1,x_2)}{\d \gamma_2} &= \frac{\partial U(x_1,x_2)}{\partial x_1}\frac{\d x_1}{\d \gamma_2} + \frac{\partial U(x_1,x_2)}{\partial x_2}\frac{\d x_2}{\d \gamma_2}\\
\frac{\d U(x_1,x_2)}{\d \gamma_2} &= \left(\frac{\partial U(x_1,x_2)}{\partial x_1}\frac{\d x_1}{\d x_2}+ \frac{\partial U(x_1,x_2)}{\partial x_2}\right)\frac{\d x_2}{\d \gamma_2}
\end{align}
Where the second line follows from the fact that $\gamma_2$ does not directly impact $x_1$ but only through $x_2$. $\frac{\d x_2}{\d \gamma_2}>0$ so that an increase in firm $2$'s benefit from market share leads to an increase in $x_2$. Thus, we conclude that if $\frac{\d x_1}{\d x_2}>0$ or if $\frac{\d x_1}{\d x_2}<0$, but close to zero, the third party should increase the incentives of firm $2$. Firm $2$ will exert more efforts, while firm $1$ either also increases hers, or only slightly reduces its efforts. In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ such that it reduces its efforts which encourages firm $1$ to increase its efforts. While the total amount of effects does necessarily decrease, firm $1$'s efforts are seen as more important than firm $2$, creating a net benefit.

In the smartphone sector we observe: a small level of loyalty and a medium amount of asymmetry. Thus, supporting the weak firm will raise overall competition leading to a welfare increase. Similar, damaging the profit margin of the leader might lead to an overall increase in the efforts if the change in the number of indifferent customers is sufficiently big.

In contrast the market for cola flavored drinks features a large amount of loyalty, with a moderate amount of asymmetry. Thus, $g'(\theta)<0$ and increasing the incentives of the weaker firm and raising the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.

\end{document}

### 2015-09-28 Paper1.tex
illustration of changes

@@
 
+look: I added a sentence here
+
 Consider the market for smartphones.
 Two firms compete over customers with heterogeneous preferences.
-For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.
+For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_1$ from each customer.
 
-Customer $k$ exhibit a preference for one of the two products that is given by $\theta_k$.
+Customer $k$ exhibits a preference for one of the two products that is given by $\theta_k$.
 $\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she has a preference for neither of the firms.
@@
 People are willing to pay a certain amount for a smartphone, but as better products enter the market, the prices for the worse products decrease so that the quality frontier always receives the same valuation.
+But if my product is $\gamma$ better than previous generation, my profits are likely to be $\gamma$ higher?
+Or is $\gamma$ not related to product quality?
 
@@
 
-If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue tu purchase its devices. Thus, the demand for firm $1$ is given by:
+If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue to purchase its devices. Thus, the demand for firm $1$ is given by:
 \begin{align*}
@@
 \end{align*}
+x is now quality?
 

### 2015-10-01 Paper1.tex
two typos corrected
small change to text 1

--- 2015-09-28 Paper1.tex
@@
 Two firms compete over customers with heterogeneous preferences.
-For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.
+Devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.
 
@@
 
-The preferences are taken as exogenously given.
-They are either derived from a non-marketable unique characteristic of the products (some people dislike the sharp shape, others love it), or they are derived from previous interactions with the firm.
-More about this later.
+Preferences are taken as exogenously given.
+They are either derived from a non-marketable unique characteristic of the products (some people dislike the sharp edges of the device, others love it), or they are derived from previous interactions with the firm.
+This can be used as the starting point for a dynamic model, but more about this later.
 
 Firms compete in R\&D efforts to increase the quality of their own products.
-While having a higher quality level helps to gain customers from the competitors, it does not help to increase the return per customer.
-People are willing to pay a certain amount for a smartphone, but as better products enter the market, the prices for the worse products decrease so that the quality frontier always receives the same valuation.
+A higher quality level helps to gain customers from the competitors.
+It can also help to increase the revenue per customer.
+People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}=0$).
 
@@
 \begin{align}
-x_1^C = g(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\\
-x_2^C = g(x_1^C-x_2^C)\frac{\gamma_2}{c_2}
+x_1^C &= g(x_1^C-x_2^C)\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
+x_2^C &= g(x_1^C-x_2^C)\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
 \end{align}
-\textbf{Here some things are missing (zero efforts, asymmetry, etc...)}Thus, w.l.g.
-we can normalize the effort costs to $1$.
+As long as $g(\cdot)>0$, efforts will be non-zero.
+If the return per customer is independent of the efforts, we can normalize the effort costs to $1$.
 Depending on the shape of $G(\cdot)$ the game might have multiple equilibria.
 To avoid uniqueness the following discussion focuses only on local changes.
+
+For the connection of the valuation and the efforts it should be assumed that $\gamma_1'(x_1)\geq 0$  and that $\gamma_1''(x_1) - c_1<0$.
+This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.
 

### 2015-10-02 Paper1.tex
added general talk about reaction in the model with increasing revenue

@@
 
-For the connection of the valuation and the efforts it should be assumed that $\gamma_1'(x_1)\geq 0$  and that $\gamma_1''(x_1) - c_1<0$.
+For the connection of the valuation and the efforts it should be assumed that $\gamma_1'(x_1)\geq 0$, such that efforts of a firm do not negatively effect its revenue, and that $\gamma_1''(x_1) - c_1<0$.
 This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.
 
+\subsection{General Case}
+The reaction function of firm $1$ to a change in the efforts of firm $2$ is given by:
+\begin{align}
+\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{\gamma}{c_1}\\
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
+A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+\end{align}
+
+Assuming that $A_i>0$, that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
+The reaction is positive if $g'(\cdot)$ is sufficiently negative.
+Then the level of competition increase sufficiently to raise the incentives to compete more.
+If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share.
+A lower market share makes extracting profits from the customers less valuable, thus making $\frac{\partial \gamma_i}{\partial x_i}$ less important.
+Thus, for small negative and large positive $g'(\cdot)$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.
+
+\subsection{Without positive effect on revue}
 The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:

### 2015-10-05 Paper1.tex
rewrote first half

@@
 
-Consider the market for smartphones.
+\section{Model Set Up}
+Consider a stylist market for smartphones.
 Two firms compete over customers with heterogeneous preferences.
@@
 
-Customer $k$ exhibit a preference for one of the two products that is given by $\theta_k$.
-$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she has a preference for neither of the firms.
-Preferences of the customers are distributed according to the cdf $G(\cdot)$ and the pdf $g(\cdot)$.
+Customer $k$ exhibits a preference for one of the two products given by $\theta_k$.
+$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she prefers neither of the firms.
+Preferences of the customers are exogenously determined and distributed according to the CDF $G(\cdot)$ and the PDF $g(\cdot)$.
 
@@
 
-Customer $k$ purchases product $2$ if and only if the difference in quality overcompensates for her own loyalty:
-$$\theta_k\geq x_1-x_2$$
+An alternative way is to let firms compete in marketing efforts.
+Marketing can either illustrate the positive characteristics of their device such that the customers' willingness to pay also increases with efforts, or it can illustrates drawbacks of the competing product such that the customers' willingness to pay remains unchanged.
 
-If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue tu purchase its devices. Thus, the demand for firm $1$ is given by:
+Customer $k$ compares the utility derived from both choices and purchases product $2$ if and only if the difference in quality overcompensates for her own loyalty.
+For simplicity ties between both choices are ignored.
+Thus customer $k$ purchases $2$ iff:
+$\theta_k\geq x_1-x_2$.
+
+If firm $1$ provides a product superior to its competitor's, only customers highly loyal to firm $2$ will continue to purchase its devices. Thus, the demand for firm $1$ is given by:
 \begin{align*}
@@
 
-Efforts cause convex costs such that the profits of both firms are given by:
+The costs of providing efforts are convex and the profits of both firms are given by:
 \begin{align}
@@
 
-The optimal effort level for both firms is thus:
+\section{Optimal Firm Behavior}
+
+The optimal effort level for both firms is:
 \begin{align}
@@
 \end{align}
-As long as $g(\cdot)>0$, efforts will be non-zero.
-If the return per customer is independent of the efforts, we can normalize the effort costs to $1$.
+As long as $g(\cdot)>0$, efforts are non-zero.
+If the return per customer is independent of the efforts, we can normalize the effort costs to $1$ without loss of generality.
 Depending on the shape of $G(\cdot)$ the game might have multiple equilibria.
@@
 
-For the connection of the valuation and the efforts it should be assumed that $\gamma_1'(x_1)\geq 0$, such that efforts of a firm do not negatively effect its revenue, and that $\gamma_1''(x_1) - c_1<0$.
+Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(x_1)\geq 0$.
+Additionally, $\gamma_1''(x_1) - c_1<0$.
 This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.

### 2015-10-07 Paper1.tex
text and spelling

@@
 
-Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(x_1)\geq 0$.
-Additionally, $\gamma_1''(x_1) - c_1<0$.
+Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(\cdot)\geq 0$.
+Additionally, $\gamma_1''(\cdot) - c_1<0$.
 This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.
@@
 \end{align}
-
-Assuming that $A_i>0$, that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
+Assuming that $A_i>0$ and that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
 The reaction is positive if $g'(\cdot)$ is sufficiently negative.
-Then the level of competition increase sufficiently to raise the incentives to compete more.
+Then the level of competition increase sufficiently to raise the incentives to compete more intensively.
 If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share.
@@
 
-\subsection{Without positive effect on revue}
+\subsection{Without positive effect on revenue}
 The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:

### 2015-10-11 Paper1.tex
Third Party
- Improving Third Party
- small changes (spelling, grammar)

@@
 % Page Layout
-%\usepackage{fullpage} %less margins
-\usepackage[margin=2cm]{geometry} %better margin control
+\usepackage[a4paper, top=2cm, bottom=2cm, left=1.5cm, right=5cm, marginparwidth=4cm]{geometry}	%For working paper
+%\usepackage[a4paper, left=1.5cm, right=5cm, marginparwidth=3cm]{geometry}
+%better margin control
 % Geometry: margin, left, right
@@
 \section{Model Set Up}
-Consider a stylist market for smartphones.
+Consider the market for smartphones.
 Two firms compete over customers with heterogeneous preferences.
-Devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.
+Devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer
 
@@
 \subsection{Without positive effect on revenue}
-The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:
+The reaction function of firm $i$ to a change in the efforts of firm $j$ is:
 \begin{align}
@@
 \end{align}
-If $g'(x_1^C-x_2^C)<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.
+If $g'(x_1^C-x_2^C)\gamma_1<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.
 
-If $-1<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
+If $-\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
 The increase in $x_2$ increases the number of indifferent customers, such that competition becomes more intense.
@@
 
-Returning to the example of the smartphone sector.
-Consider $g(\cdot)$ such that it is $-1<g'(\theta)$ for all $\theta$.
-Additionally, most customers are centered in the middle with smaller tails.
-This can be described by: $g'(0)=0$ and $g'(\theta)<0, \theta>0$,$g'(\theta)<0, \theta<0$.
+Returning to the example of the smartphone sector, we consider a distribution that satisfies $-\frac{1}{\gamma_1}<g'(\theta)<\frac{1}{\gamma_1}$ for all $\theta$.\marginpar{I need to address symmetry earlier in the text.} Additionally, most customers are centered in the middle with only few highly loyal customers.
+This can be described by $g'(0)=0$ and $g'(\theta)<0, \theta>0; g'(\theta)<0, \theta<0$.
 Most customer are willing to switch to the superior product, while a small number has some inherent preference for one.
+
+\section{Third Party}
 
@@
 The utility of the research and development expenses of the firm is given by $U(x_1,x_2)$ with $\frac{\partial U(x_1,x_2)}{\partial x_1},\frac{\partial U(x_1,x_2)}{\partial x_2}>0$.
-This is achieved my affecting the incentives of the firms.
-To simplify the problem assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm with $\gamma_1>\gamma_2$.
+This is achieved by affecting the incentives of the firms.
+To simplify the problem we assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm with $\gamma_1\geq\gamma_2$.
 The optimal $\gamma_2$ is given by:

### 2015-10-12 Paper1.tex
Rewrote the Third Party section. Small corrections

@@
 
-Now consider a third party, that is maximizing a function of $x_1, x_2$.
-The utility of the research and development expenses of the firm is given by $U(x_1,x_2)$ with $\frac{\partial U(x_1,x_2)}{\partial x_1},\frac{\partial U(x_1,x_2)}{\partial x_2}>0$.
-This is achieved by affecting the incentives of the firms.
-To simplify the problem we assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm with $\gamma_1\geq\gamma_2$.
+Now consider a third party, that is maximizing the efforts $x_1$ and $x_2$, weighted with some function.
+The utility derived from the R\&D expenditures is given by $U(x_1,x_2)$ with $\frac{\partial U(x_1,x_2)}{\partial x_1},\frac{\partial U(x_1,x_2)}{\partial x_2}>0$.
+The third party is able to affect the incentives of the firms.
+To simplify the problem we assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm ($\gamma_1\geq\gamma_2$).
 The optimal $\gamma_2$ is given by:
@@
 \end{align}
-Where the second line follows from the fact that $\gamma_2$ does not directly impact $x_1$ but only through $x_2$.
-$\frac{\d x_2}{\d \gamma_2}>0$ so that an increase in firm $2$'s benefit from market share leads to an increase in $x_2$.
-Thus, we conclude that if $\frac{\d x_1}{\d x_2}>0$ or if $\frac{\d x_1}{\d x_2}<0$, but close to zero, the third party should increase the incentives of firm $2$.
-Firm $2$ will exert more efforts, while firm $1$ either also increases hers, or only slightly reduces its efforts.
-In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ such that it reduces its efforts which encourages firm $1$ to increase its efforts.
+The second line follows from the fact that $\gamma_2$ does not directly impact $x_1$ but only through $x_2$.
+An increase in the incentives of firm $2$ leads to an increase of its efforts such that $\frac{\d x_2}{\d \gamma_2}>0$.
+
+Thus, if the reaction function is positive or only slightly negative an increase in the incentives of the weaker firm ($2$) leads to an increase in the total efforts of both firms.
+Firm $2$ will exert more efforts which in turn will encourage firm $1$ to also increases hers, or only slightly reduces its efforts.
+
+In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and/or if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ such that it reduces its efforts which encourages firm $1$ to increase its efforts.
 While the total amount of effects does necessarily decrease, firm $1$'s efforts are seen as more important than firm $2$, creating a net benefit.
+If the effort do not change the firm's profit extraction, the latter case requires that $\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$.
 
@@
 Similar, damaging the profit margin of the leader might lead to an overall increase in the efforts if the change in the number of indifferent customers is sufficiently big.
+Here moving closer to symmetry increases competition intensity.
 
-In contrast the market for cola flavored drinks features a large amount of loyalty, with a moderate amount of asymmetry.
-Thus, $g'(\theta)<0$ and increasing the incentives of the weaker firm and raising the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.
+In contrast, the market for cola-flavored soft-drinks features a large amount of loyalty, with a moderate amount of asymmetry.
+Thus, $g'(\theta)<0$ and increasing the incentives of the weaker firm or raising the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.
+
+\subsection{Value-Augmenting Efforts}
+If the efforts of the firm also augment its profit extraction from customers, the reaction function becomes:
+\begin{align}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
+A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+\end{align}
+
+A sufficiently positive $g'(\theta)$ leads to an decrease in the effort of firm $1$ in response to an increase in the efforts of firm $2$.
+However, the reaction is now also determined by the changes to the market share.
+An increase in the efforts of firm $2$ leads to a decrease in the market shares of firm $1$.
+This lowers it's incentives to use high efforts to extract monetary value from the firms.
+By encouraging the laggards in the smartphone sector the third party also reduces the market share of the leading firms, who will then invest less in R\&D.
+
+\section{Other aspects}
+\begin{itemize}
+	\item Market shares determine investments. Are returns convex or concave?
+	\item Customers profit from investment. The large firm has more customers. If it invests more, it helps more people. 
+	\item What is the social optimum?
+	\item Switching costs?
+\end{itemize}
 

### 2015-10-15 Paper1.tex
some comments and suggestions

@@
 Customer $k$ exhibits a preference for one of the two products given by $\theta_k$.
-$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she prefers neither of the firms.
+$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she is indifferent between the firms.
 Preferences of the customers are exogenously determined and distributed according to the CDF $G(\cdot)$ and the PDF $g(\cdot)$.
+without atoms and $g$ is continuously differentiable
 
@@
 It can also help to increase the revenue per customer.
-People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}=0$).
+People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}=0$).$>0$?
 
@@
 Customer $k$ compares the utility derived from both choices and purchases product $2$ if and only if the difference in quality overcompensates for her own loyalty.
-For simplicity ties between both choices are ignored.
+For simplicity ties between both choices are ignored has measure 0.
 Thus customer $k$ purchases $2$ iff:
@@
 Depending on the shape of $G(\cdot)$ the game might have multiple equilibria.
-To avoid uniqueness the following discussion focuses only on local changes.
+To avoid having to assume uniqueness the following discussion focuses only on local changes.
 
@@
 Additionally, $\gamma_1''(\cdot) - c_1<0$.
-This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.
+This implies that efforts don't decrease the valuation of the product and that in lieu ?without?
+of competition the optimal level of efforts is finite.
 
@@
 Assuming that $A_i>0$ and that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
-The reaction is positive if $g'(\cdot)$ is sufficiently negative.
-Then the level of competition increase sufficiently to raise the incentives to compete more intensively.
+The reaction is positive if $g'(\cdot)$ is sufficiently negative ?but that also affects the sign of $A_i$?.
+Then the level of competition ?measured how?
+increase sufficiently to raise the incentives to compete more intensively.
 If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share.
@@
 \subsection{Without positive effect on revenue}
+?do this subsection first: easier for the reader?
+
 The reaction function of firm $i$ to a change in the efforts of firm $j$ is:
@@
 If $g'(x_1^C-x_2^C)\gamma_1<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.
+?effect of $x_1$ on $x_1$ follows from $dx_1/dx_2$?
 
@@
 Thus, $g'(\theta)<0$ and increasing the incentives of the weaker firm or raising the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.
+but $g'(\theta) > 0$ for a U-shape with 2 the disadvantaged firm?
 

### 2015-10-18 Paper1.tex
Example Uniform
Added small section on the implications of having a uniform distribution

@@
 
+\section{Examples}
+\subsection{Basic Case - Uniform Distribution}
+First consider the basic case of a uniform distribution of customers. Thus $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The solutions to the firms problem become:
+
+\begin{align}
+x_1^C &= \tilde{g}\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
+x_2^C &= \tilde{g}\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
+\end{align}
+
+The reaction function equals:
+\begin{align*}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left( -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
+A_i &= 1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+\end{align*}
+
+If the efforts don't affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\frac{\gamma_i}{c_i}$ and thus proportional to the value and the cost ratio.
+Furthermore, the efforts are independent of the competitors efforts.
+
+If the firm also derive value from the efforts then the reaction is always negative.
+A higher effort by firm $2$ leads to a lower market share of firm $1$, which reduces its incentives to exert efforts.
+
 \section{Other aspects}

### 2015-10-20 Paper1.tex
added changes from comments

@@
 Preferences of the customers are exogenously determined and distributed according to the CDF $G(\cdot)$ and the PDF $g(\cdot)$.
-without atoms and $g$ is continuously differentiable
+$G(\cdot)$ is assumed twice continuously differentiable such that $g(\cdot)$ is continuously differentiable and the distribution lacks atoms.
 
@@
 It can also help to increase the revenue per customer.
-People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}=0$).$>0$?
+People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}>0$).
 
@@
 Customer $k$ compares the utility derived from both choices and purchases product $2$ if and only if the difference in quality overcompensates for her own loyalty.
-For simplicity ties between both choices are ignored has measure 0.
-Thus customer $k$ purchases $2$ iff:
+The distribution has no atoms, such that ties occur with measure $0$.
+Thus customer $k$ purchases $2$ if and only if:
 $\theta_k\geq x_1-x_2$.
@@
 Additionally, $\gamma_1''(\cdot) - c_1<0$.
-This implies that efforts don't decrease the valuation of the product and that in lieu ?without?
-of competition the optimal level of efforts is finite.
+This implies that efforts don't decrease the valuation of the product and that without of competition the optimal level of efforts is finite.
+
+\subsection{Special Case: Per Customer Revenue independent of Efforts}
+
+The reaction function of firm $i$ to a change in the efforts of firm $j$ is:
+\begin{align}
+\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
+\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}}{1-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}}
+\end{align}
+In this case the costs can be normalized to $1$ by setting the revenue per customer to $\frac{\gamma_1}{c_1}$.
+If $g'(x_1^C-x_2^C)\gamma_1 > 1$ the market cannot be in equilibrium as the second order condition for the optimal efforts of firm $1$  implies that the optimal efforts are not a maximum.
+
+If $-\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
+The increase in $x_2$ increases the number of indifferent customers, such that competition becomes more intense.
+If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.
+
+Returning to the example of the smartphone sector, we consider a distribution that satisfies $-\frac{1}{\gamma_1}<g'(\theta)<\frac{1}{\gamma_1}$ for all $\theta$.\marginpar{I need to address symmetry earlier in the text.} Additionally, most customers are centered in the middle with only few highly loyal customers.
+This can be described by $g'(0)=0$ and $g'(\theta)<0, \theta>0; g'(\theta)<0, \theta<0$.
+Most customer are willing to switch to the superior product, while a small number has some inherent preference for one.
 
@@
 Assuming that $A_i>0$ and that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
-The reaction is positive if $g'(\cdot)$ is sufficiently negative ?but that also affects the sign of $A_i$?.
-Then the level of competition ?measured how?
-increase sufficiently to raise the incentives to compete more intensively.
+The reaction is positive if $g'(\cdot)$ is sufficiently negative.
+In this case also $A_i>0$.
+Then the competition intensity described by $g(\theta^*)$ increases sufficiently to raise the incentives to compete more intensively.
 If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share.
@@
 Thus, for small negative and large positive $g'(\cdot)$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.
-
-\subsection{Without positive effect on revenue}
-?do this subsection first: easier for the reader?
-
-The reaction function of firm $i$ to a change in the efforts of firm $j$ is:
-\begin{align}
-\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\gamma_1\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
-\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\gamma_1}{1+g'(x_1^C-x_2^C)\gamma_1}
-\end{align}
-If $g'(x_1^C-x_2^C)\gamma_1<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.
-?effect of $x_1$ on $x_1$ follows from $dx_1/dx_2$?
-
-If $-\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
-The increase in $x_2$ increases the number of indifferent customers, such that competition becomes more intense.
-If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.
-
-Returning to the example of the smartphone sector, we consider a distribution that satisfies $-\frac{1}{\gamma_1}<g'(\theta)<\frac{1}{\gamma_1}$ for all $\theta$.\marginpar{I need to address symmetry earlier in the text.} Additionally, most customers are centered in the middle with only few highly loyal customers.
-This can be described by $g'(0)=0$ and $g'(\theta)<0, \theta>0; g'(\theta)<0, \theta<0$.
-Most customer are willing to switch to the superior product, while a small number has some inherent preference for one.
+%address the sign of A_i better.
 
@@
 In contrast, the market for cola-flavored soft-drinks features a large amount of loyalty, with a moderate amount of asymmetry.
-Thus, $g'(\theta)<0$ and increasing the incentives of the weaker firm or raising the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.
-but $g'(\theta) > 0$ for a U-shape with 2 the disadvantaged firm?
+Thus, $g'(\theta)>0$ and increasing the incentives of the weaker firm or reducing the incentives of the leader causes a decrease in competition and an overall decrease in total efforts.
 

### 2015-10-20 Paper1.tex
improved section about uniform distribution

@@
 \begin{align}
-\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{\gamma}{c_1}\\
+\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{1}{c_1}\\
 \frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
 \end{align}
@@
 \frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
 \end{align}
@@
 \subsection{Basic Case - Uniform Distribution}
-First consider the basic case of a uniform distribution of customers. Thus $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The solutions to the firms problem become:
-
+First, consider the basic case of a uniform distribution of customers. Thus $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The solutions to the firms problem becomes:
 \begin{align}
+\begin{split}
 x_1^C &= \tilde{g}\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
 x_2^C &= \tilde{g}\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
+\end{split}
 \end{align}
-
-The reaction function equals:
+The reaction function is given by:
 \begin{align*}
 \frac{\d x_1}{\d x_2} &= A_i^{-1} \left( -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
+A_i &= 1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
 \end{align*}
+If the efforts do not affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\frac{\gamma_i}{c_i}$ and thus proportional to the value and the cost ratio.
+Most importantly, the efforts are independent of the competitors efforts.
+Firms compete for market shares, but their optimal decision are independent of the other firms decision.
 
-If the efforts don't affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\frac{\gamma_i}{c_i}$ and thus proportional to the value and the cost ratio.
-Furthermore, the efforts are independent of the competitors efforts.
+If the firm also derive value from the efforts, the reaction is always negative.
+A higher effort by firm $2$ leads to a lower market share of firm $1$, which reduces its incentives to exert efforts.
+Market share is the dominant motivator to perform product improvement and a smaller one leads to less incentives to innovate.
 
-If the firm also derive value from the efforts then the reaction is always negative.
-A higher effort by firm $2$ leads to a lower market share of firm $1$, which reduces its incentives to exert efforts.
+Can the increase of firm $2$'s efforts in this case lead to an increase of total efforts? This would require that $\frac{\d x_1}{\d x_2} >-1$.
+\begin{align*}
+-1<\frac{\d x_1}{\d x_2}&\leq0\\
+0\leq\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}&<1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+\end{align*}
+Thus, total efforts only increase if the affect of $x_1$ on the value extraction is very small.
+If $\frac{\partial \gamma_1}{\partial x_1}=0$ it holds as the efforts are independent of the market share.
+However, if the efforts are very important in extracting value from the customers an increase in the efforts of any party leads to a decrease in the total efforts in the market.
 

### 2015-10-20 Paper1.tex
added loyalty example

@@
 
+\subsection{Loyalty}
+No consider the case of both firms having a loyal customer base such that $g'(\theta)>0$ to the right of the center.
+Firm $2$ is the disadvantaged firm, with $x_2<x_1$.
+This can be due to a difference in costs or value extraction.
+The reaction function is:
+
+\begin{align}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \underbrace{\left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\right.}_{>0} - \left.g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
+A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+\end{align}
+Thus, the sign of the reaction of firm $1$ depends on the relative expression of the changes in competition.
+If the intensity of competition increases significantly in response to a reduction of firm $2$'s efforts, firm $1$ will raise its efforts.
+Similarly, if the value extraction is fixed, an increase in the efforts of firm $1$ will raise firm $2$'s incentive to exert efforts.
+Paradoxically, supporting the market leader raises the efforts of the laggard, and raising the efforts of the laggards, reduces the efforts of the market leader.
+This is precisely the opposite of what we expect.
+
+This effect is affected by the changes to the value extraction.
+In general the firm that gains an advantage has a higher incentives to raise its efforts and the losing firm gains incentives to lower its efforts.
+This can partially offset the result in the previous paragraph.
+
 \section{Other aspects}

### 2015-10-23 Paper1.tex
added comparison of uniform and double peaked, added a small dynamic discussion (rough and uncomplete), added an empty bib file

@@
 \title{Asymmetric Agents and their Willingness to Fight\\
-	Customer Loyalty and its Impact on Competition}
+	{\Large Customer Loyalty and its Impact on Competition}}
 
@@
 Consider the market for smartphones.
-Two firms compete over customers with heterogeneous preferences.
-Devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer
+Two firms $i\in\{1,2\}$ compete over customers with heterogeneous preferences.
+Devices are sold at an exogenously given price such that firm $i$ derives a profit of $\gamma_i$ from each customer
 
+The demand side is given by a number of customers with unit mass and a heterogeneous level of loyalty towards one of the brands.
 Customer $k$ exhibits a preference for one of the two products given by $\theta_k$.
-$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she is indifferent between the firms.
-Preferences of the customers are exogenously determined and distributed according to the CDF $G(\cdot)$ and the PDF $g(\cdot)$.
+$\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k= 0$ that she is indifferent between the firms.
+Preferences of the customers are exogenously determined and distributed according to the cdf $G(\cdot)$ and the pdf $g(\cdot)$.
 $G(\cdot)$ is assumed twice continuously differentiable such that $g(\cdot)$ is continuously differentiable and the distribution lacks atoms.
@@
 It can also help to increase the revenue per customer.
-People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while there willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}>0$).
+People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while their willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}>0$).
 
@@
 
-The optimal effort level for both firms is:
+The optimal effort level for both firms and the indifferent customer are:
 \begin{align}
+\begin{split}
 x_1^C &= g(x_1^C-x_2^C)\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
 x_2^C &= g(x_1^C-x_2^C)\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
+\end{split}\\
+\theta^* &=  g(x_1^C-x_2^C)\left(\frac{\gamma_1}{c_1}-\frac{\gamma_2}{c_2}\right) + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} - \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
 \end{align}
@@
 Additionally, $\gamma_1''(\cdot) - c_1<0$.
-This implies that efforts don't decrease the valuation of the product and that without of competition the optimal level of efforts is finite.
+Efforts do not decrease the valuation of the product but the return is either concave or not too convex such that even without competition the optimal effort level would be finite.
 
-\subsection{Special Case: Per Customer Revenue independent of Efforts}
+\subsection{Special Case: Per Customer Revenue Independent of Efforts}
 
@@
 
-This effect is affected by the changes to the value extraction.
+The strength of the effect depends on the changes to the value extraction.
 In general the firm that gains an advantage has a higher incentives to raise its efforts and the losing firm gains incentives to lower its efforts.
@@
 
+\subsection{Comparision}
+
+If customer loyalty is missing from the model, the only channel through which the efforts of the firms interact is the value extraction.
+If firm $2$ expands its market share at the expenses of firm $1$, firm $2$ has an additional incentive to have higher efforts and firm $1$ to reduce its efforts.
+This fact does not depend on the market shares, so supporting the weak firm always reduces the efforts of the leader.
+
+The effect of total efforts depends on the relative size and the shape of the value extraction function.
+If the value extraction rate is concave, a higher level of total efforts can be achieved with more symmetric efforts.
+(intuitively yes, but formal proof necessary).
+
+In comparison, the model with customer loyalty features an additional channel.
+Any change to the efforts leads to a change in the number of critical customers, thus effecting the intensity of competition.
+A slight level of asymmetry implies that firms are competing over the home market of firm $2$, and have a high incentive to compete heavily.
+
+\section{A small outlook to dynamics}
+This is not meant to be part of the paper, but maybe it is interesting.
+Consider for a small though experiment that some dynamics are at work.
+More precisely, a customer that buys from one firm, will become more likely to do so over time.
+Mathematically, for $\theta<\theta^*$ $F_{t+1}(\theta)>F_t(\theta)$ and for $\theta>\theta^*$ $F_{t+1}(\theta)<F_t(\theta)$.
+
+In the next period, both firms exert less efforts as $g(\theta^*)$ goes down.
+However, the stronger firm ($1$) reacts more strongly to this, shifting market shares to firm $2$.
+Ironically, the market shares become more equal.
+It is important to note, that this builds on myopic firms.
 \section{Other aspects}

### 2015-10-26 Paper1.tex

@@
 Two firms $i\in\{1,2\}$ compete over customers with heterogeneous preferences.
-Devices are sold at an exogenously given price such that firm $i$ derives a profit of $\gamma_i$ from each customer
+Devices are sold at an exogenously given price such that firm $i$ derives a profit of $\gamma_i$ from each customer.
 
@@
 It can also help to increase the revenue per customer.
-People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy, while their willingness to pay could remain unchanged ($\frac{\partial \gamma_i}{\partial x_i}=0$) it will often increase ($\frac{\partial \gamma_i}{\partial x_i}>0$).
+People are willing to pay a certain amount for a smartphone, and the quality might have a strong impact on their decision which device to buy.
+However, their willingness to pay might be independent of the quality level ($\frac{\partial \gamma_i}{\partial x_i}=0$) or it might be increasing in the efforts ($\frac{\partial \gamma_i}{\partial x_i}>0$).
 
@@
 The distribution has no atoms, such that ties occur with measure $0$.
-Thus customer $k$ purchases $2$ if and only if:
-$\theta_k\geq x_1-x_2$.
+Thus customer $k$ purchases $2$ if and only if: $\theta_k\geq x_1-x_2$.
+Let the indifferent customer be determined by $\theta^* \equiv x_1-x_2$.
 
-If firm $1$ provides a product superior to its competitor's, only customers highly loyal to firm $2$ will continue to purchase its devices. Thus, the demand for firm $1$ is given by:
-\begin{align*}
-G(x_1-x_2)
-\end{align*}
-
+If firm $1$ provides a product superior to its competitor's, only customers highly loyal to firm $2$ are purchasing from firm $2$.
+The demand for firm $1$ is thus given by $G(x_1-x_2)$.
 The costs of providing efforts are convex and the profits of both firms are given by:
 \begin{align}
+\begin{split}
 	G(x_1-x_2)\gamma_1 - c_1x_1^2/2\\
 	\big(1-G(x_1-x_2)\big)\gamma_2 - c_2x_2^2/2
+\end{split}
 \end{align}
@@
 x_2^C &= g(x_1^C-x_2^C)\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
-\end{split}\\
+\end{split}
+\end{align}
+\begin{align}
 \theta^* &=  g(x_1^C-x_2^C)\left(\frac{\gamma_1}{c_1}-\frac{\gamma_2}{c_2}\right) + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} - \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
@@
 As long as $g(\cdot)>0$, efforts are non-zero.
-If the return per customer is independent of the efforts, we can normalize the effort costs to $1$ without loss of generality.
-Depending on the shape of $G(\cdot)$ the game might have multiple equilibria.
+For simplicity we normalize the costs of effort provision to $1$ without loss of generality, for both firms, by defining: $\gamma_i(x_i)\equiv \gamma_i(x_i)/c_i$.
+Depending on the shape of $G(\cdot)$ the game might feature multiple equilibria.
 To avoid having to assume uniqueness the following discussion focuses only on local changes.
 
-Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(\cdot)\geq 0$.
-Additionally, $\gamma_1''(\cdot) - c_1<0$.
-Efforts do not decrease the valuation of the product but the return is either concave or not too convex such that even without competition the optimal effort level would be finite.
+Efforts either increase the return per customers or leave it unchanged such that $\gamma_i'(x_i)\geq 0$.
+Additionally, the return per customer of sufficiently concave such that $\gamma_i''(x_i) - 1<0$.
+The return is either concave or not too convex such that even without competition the optimal effort level would be finite.\footnote{For simplicity this is assumed to be the case globaly.}
 
 \subsection{Special Case: Per Customer Revenue Independent of Efforts}
-
-The reaction function of firm $i$ to a change in the efforts of firm $j$ is:
+The reaction function of firm $1$ to a change in the efforts of firm $2$ is:
 \begin{align}
-\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
-\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}}{1-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}}
+\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\gamma_1\left(\frac{\d x_1^C}{\d x_2}-1\right)\nonumber\\
+\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\gamma_1}{1-g'(x_1^C-x_2^C)\gamma_1}
+\label{eqn:reactionSpecialCase}
 \end{align}
-In this case the costs can be normalized to $1$ by setting the revenue per customer to $\frac{\gamma_1}{c_1}$.
-If $g'(x_1^C-x_2^C)\gamma_1 > 1$ the market cannot be in equilibrium as the second order condition for the optimal efforts of firm $1$  implies that the optimal efforts are not a maximum.
+If $g'(x_1^C-x_2^C)\gamma_1 > 1$, the market cannot be in equilibrium as the second order condition for the optimal efforts of firm $1$ implies that the efforts are not at a maximum.
+Consequently, the denominator in equation \ref{eqn:reactionSpecialCase} is positive.
 
 If $-\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
-The increase in $x_2$ increases the number of indifferent customers, such that competition becomes more intense.
+The increase in $x_2$ raises the number of indifferent customers, such that competition becomes more intense.
 If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.
+\marginpar{add a sketch here}
 
-Returning to the example of the smartphone sector, we consider a distribution that satisfies $-\frac{1}{\gamma_1}<g'(\theta)<\frac{1}{\gamma_1}$ for all $\theta$.\marginpar{I need to address symmetry earlier in the text.} Additionally, most customers are centered in the middle with only few highly loyal customers.
-This can be described by $g'(0)=0$ and $g'(\theta)<0, \theta>0; g'(\theta)<0, \theta<0$.
-Most customer are willing to switch to the superior product, while a small number has some inherent preference for one.
+Returning to the example of the smartphone sector, we consider a distribution that satisfies $-\frac{1}{\gamma_1}<g'(\theta)<\frac{1}{\gamma_2}$\footnote{This assures us that the second order condition is satisfied for both firms.} for all $\theta$.\marginpar{I need to address symmetry earlier in the text.} Additionally, most customers are centered in the middle with only a few highly loyal customers.
+This can be described by $g'(0)=0$ and $g'(\theta)<0~\forall \theta>0$ and $g'(\theta)<0~\forall \theta<0$.
+Most customer are willing to switch to the superior product, but a small number has some inherent preference for one.
 
 \subsection{General Case}
-The reaction function of firm $1$ to a change in the efforts of firm $2$ is given by:
+Now, we analyze the more general case with $\frac{\partial \gamma_1}{\partial x_1}\geq 0$. The reaction function of firm $1$ to a change in the efforts of firm $2$ is given by:
 \begin{align}
-\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{1}{c_1}\\
-\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+\frac{\d x_1}{\d x_2} &= g'(\theta^*)\left(\tfrac{\d x_1}{\d x_2}-1\right)\gamma_1 + g(\theta^*)\left(2\tfrac{\d x_1}{\d x_2}-1\right)\tfrac{\partial \gamma_1}{\partial x_1} + G(\theta^*)\tfrac{\partial^2 \gamma_1}{\partial^2 x_1}\tfrac{\d x_1}{\d x_2}\nonumber\\
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(\theta^*)\gamma_1- g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}\right)\\
+A_i &= 1 - g'(\theta^*)c_1-2g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}-G(\theta^*)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
 \end{align}
-Assuming that $A_i>0$ and that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$.
-The reaction is positive if $g'(\cdot)$ is sufficiently negative.
-In this case also $A_i>0$.
-Then the competition intensity described by $g(\theta^*)$ increases sufficiently to raise the incentives to compete more intensively.
+Similar to before, the second order condition implies that $A_i>0$ and by assumption $\frac{\partial \gamma_1}{\partial x_1}>0$.
+The sign of the reaction function depends on $g'(\cdot)$ and $g(\cdot)$, and $\frac{\partial \gamma_1}{\partial x_1}$ and $\gamma_i$.
+In fact the reaction depends on the change to the return of the indifferent customer.
+The reaction is positive if $\frac{\partial}{\partial x_1} g(\theta^*)\gamma_1<0$.
+The competition intensity described by $g(\theta^*)$ increases sufficiently to raise the incentives to compete more intensively.
 If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share.
 A lower market share makes extracting profits from the customers less valuable, thus making $\frac{\partial \gamma_i}{\partial x_i}$ less important.
-Thus, for small negative and large positive $g'(\cdot)$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.
-%address the sign of A_i better.
+Thus, for $\frac{\partial}{\partial x_1} g(\theta^*)\gamma_1>0$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.
+
+The interpretation is not straightforward.
+If $\frac{\partial}{\partial x_1} g(\theta^*)\gamma_1<0$, an increase of the efforts of firm $1$ would lead to a decrease of the revenue extracted from the indifferent customers.
+This means that firm $1$ has a natural tendency to reduce its efforts and a negative shock will lead to a reduction of its efforts.
+\marginpar{\footnotesize doesn't quite fit, need to think about this more.}
 
@@
 
-Now consider a third party, that is maximizing the efforts $x_1$ and $x_2$, weighted with some function.
+Now consider a third party, that is maximizing the efforts $x_1$ and $x_2$, weighted by some function.
 The utility derived from the R\&D expenditures is given by $U(x_1,x_2)$ with $\frac{\partial U(x_1,x_2)}{\partial x_1},\frac{\partial U(x_1,x_2)}{\partial x_2}>0$.
 The third party is able to affect the incentives of the firms.
-To simplify the problem we assume that the third party intervenes in $\gamma_2$ and that firm $2$ is the disadvantaged firm ($\gamma_1\geq\gamma_2$).
+To simplify the problem we assume that the third party intervenes by scaling $\gamma_2$ and that firm $2$ is the disadvantaged firm ($\gamma_1\geq\gamma_2$).
 The optimal $\gamma_2$ is given by:
@@
 \end{align}
-The second line follows from the fact that $\gamma_2$ does not directly impact $x_1$ but only through $x_2$.
+The second line follows from the fact that $\gamma_2$ does not directly impact $x_1$, but only through the change it causes in $x_2$.
 An increase in the incentives of firm $2$ leads to an increase of its efforts such that $\frac{\d x_2}{\d \gamma_2}>0$.
@@
 Thus, if the reaction function is positive or only slightly negative an increase in the incentives of the weaker firm ($2$) leads to an increase in the total efforts of both firms.
-Firm $2$ will exert more efforts which in turn will encourage firm $1$ to also increases hers, or only slightly reduces its efforts.
+Firm $2$ will exert more efforts which in turn will encourage firm $1$ to also increases, or only slightly reduces its efforts.
 
-In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and/or if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ such that it reduces its efforts which encourages firm $1$ to increase its efforts.
+In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and/or if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ to reduces its efforts and encourage firm $1$ to increase its efforts.
 While the total amount of effects does necessarily decrease, firm $1$'s efforts are seen as more important than firm $2$, creating a net benefit.
-If the effort do not change the firm's profit extraction, the latter case requires that $\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$.
+If the effort do not change the firm's profit extraction, the latter case requires that $\frac{1}{\gamma_1}<g'(\theta^*)<0$.
 
@@
 If the efforts of the firm also augment its profit extraction from customers, the reaction function becomes:
-\begin{align}
-\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
-\end{align}
+\begin{align*}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(\theta^*)\gamma_1 - g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}\right)\\
+A_i &= 1 - g'(\theta^*)\frac{\gamma_1}{c_1}-2g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}-G(\theta^*)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
+\end{align*}
 
@@
 An increase in the efforts of firm $2$ leads to a decrease in the market shares of firm $1$.
-This lowers it's incentives to use high efforts to extract monetary value from the firms.
-By encouraging the laggards in the smartphone sector the third party also reduces the market share of the leading firms, who will then invest less in R\&D.
+This lowers its incentives to use high efforts to extract monetary value from the firms.
+By encouraging the laggards in the smartphone sector, the third party also reduces the market share of the leading firms, who will then invest less in R\&D.
 
@@
 \subsection{Basic Case - Uniform Distribution}
-First, consider the basic case of a uniform distribution of customers. Thus $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The solutions to the firms problem becomes:
+First, consider the basic case of a uniform distribution of customers with $g(\theta)\equiv\tilde{g}$ and $g'(\cdot)=0$. The optimal efforts are:
 \begin{align}
 \begin{split}
-x_1^C &= \tilde{g}\frac{\gamma_1}{c_1} + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\\
-x_2^C &= \tilde{g}\frac{\gamma_2}{c_2} + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}\frac{1}{c_2}
+x_1^C &= \tilde{g}\gamma_1 + G(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\\
+x_2^C &= \tilde{g}\gamma_2 + \big(1-G(x_1-x_2)\big)\frac{\partial \gamma_2}{\partial x_2}
 \end{split}
@@
 \begin{align*}
-\frac{\d x_1}{\d x_2} &= A_i^{-1} \left( -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \left( -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\right)\\
+A_i &= 1 -2\tilde{g}\frac{\partial \gamma_1}{\partial x_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
 \end{align*}
-If the efforts do not affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\frac{\gamma_i}{c_i}$ and thus proportional to the value and the cost ratio.
+If the efforts do not affect the value extraction of the firms, the optimal efforts of the firms are given by $\tilde{g}\gamma_i$ and are thus proportional to the value extracted from the indifferent customer.
 Most importantly, the efforts are independent of the competitors efforts.
@@
 -1<\frac{\d x_1}{\d x_2}&\leq0\\
-0\leq\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}&<1 -\tilde{g}\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+0\leq\tilde{g}\frac{\partial \gamma_1}{\partial x_1}&<1 -2\tilde{g}\frac{\partial \gamma_1}{\partial x_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
 \end{align*}
@@
 \begin{align}
-\frac{\d x_1}{\d x_2} &= A_i^{-1} \underbrace{\left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\right.}_{>0} - \left.g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
-A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
+\frac{\d x_1}{\d x_2} &= A_i^{-1} \underbrace{\left(-g'(\theta^*)\right.}_{>0} - \left.g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}\right)\\
+A_i &= 1 - g'(\theta^*)-g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}-G(\theta^*)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
 \end{align}

### 2015-10-26 Paper1.tex
some suggestions

@@
 \end{align}
+
+\marginpar{I am not sure I understand the third equation; how does this relate to $\theta^{*} = x_1 - x_2$???; what does the superscript $C$ mean?}
+
 As long as $g(\cdot)>0$, efforts are non-zero.
@@
 If $-\frac{1}{\gamma_1}<g'(x_1^C-x_2^C)<0$ this expression is positive, such that an increase in $x_2$ leads to an increase in $x_1$ and thus an overall escalation.
-The increase in $x_2$ raises the number of indifferent customers, such that competition becomes more intense.
-If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.
+The increase in $x_2$ raises the number of indifferent customers, such that competition becomes more intense.\marginpar{explicitly say what your definition of competition intensity is: $dx_1/dx_2 >0$?
+or $d(x_{1}+x_2)/dx_2>0$ or increase in number of indifferent consumers?
+In the latter case, it should be something like marginal over infra-marginal?} If $g'(x_1^C-x_2^C)>0$ this expression is negative and an increase in $x_2$ leads to crowding out of $x_1$.
 \marginpar{add a sketch here}
@@
 This can be described by $g'(0)=0$ and $g'(\theta)<0~\forall \theta>0$ and $g'(\theta)<0~\forall \theta<0$.
-Most customer are willing to switch to the superior product, but a small number has some inherent preference for one.
+Most customer are willing to switch to the superior product, but a small number has some inherent preference for one.\marginpar{both $g'<0$?}
 
@@
 A_i &= 1 - g'(\theta^*)c_1-2g(\theta^*)\frac{\partial \gamma_1}{\partial x_1}-G(\theta^*)\frac{\partial^2 \gamma_1}{\partial^2 x_1}
-\end{align}
+\end{align} \marginpar{why subscript $i$? $A_1$?}
 Similar to before, the second order condition implies that $A_i>0$ and by assumption $\frac{\partial \gamma_1}{\partial x_1}>0$.
@@
 \marginpar{\footnotesize doesn't quite fit, need to think about this more.}
+
+\marginpar{I would say: two reasons to raise $x1$: higher market share ($g$) and higher margin over existing market share. Relevant effect: how does $x_2$ affect these two margins?}
 
@@
 
-In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and/or if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ the third party should reduce the incentives of firm $2$ to reduces its efforts and encourage firm $1$ to increase its efforts.
+In contrast, if $\frac{\d x_1}{\d x_2}\ll0$ and/or if $\frac{\partial U(x_1,x_2)}{\partial x_1}\gg \frac{\partial U(x_1,x_2)}{\partial x_2}$ ???and $dx_1/dx_2<0$???
+the third party should reduce the incentives of firm $2$ to reduces its efforts and encourage firm $1$ to increase its efforts.
 While the total amount of effects does necessarily decrease, firm $1$'s efforts are seen as more important than firm $2$, creating a net benefit.
@@
 
-In the smartphone sector we observe: a small level of loyalty and a medium amount of asymmetry.
-Thus, supporting the weak firm will raise overall competition leading to a welfare increase.
-Similar, damaging the profit margin of the leader might lead to an overall increase in the efforts if the change in the number of indifferent customers is sufficiently big.
+In the smartphone sector ???does $x$ affect $\gamma$???
+we observe: a small level of loyalty and a medium amount of asymmetry.
+Thus, supporting the weak firm will raise overall competition ???using which definition?
+same as above???
+leading to a welfare increase.
+Similar, damaging the profit margin of the leader ???but $\gamma_{2}\leq \gamma_1$???
+might lead to an overall increase in the efforts if the change in the number of indifferent customers is sufficiently big.
 Here moving closer to symmetry increases competition intensity.
+
+???give more details for these examples: $d\gamma/dx >0$; what is effect of assumptions on $dx_1/dx_{2}$???
 
@@
 \end{align*}
+
+???why repeat the expressions???
 
@@
 
+???so what is the benchmark that readers expect; strategic substitutes???
+
 \subsection{Loyalty}
@@
 If customer loyalty is missing from the model, the only channel through which the efforts of the firms interact is the value extraction.
-If firm $2$ expands its market share at the expenses of firm $1$, firm $2$ has an additional incentive to have higher efforts and firm $1$ to reduce its efforts.
+If firm $2$ expands its market share at the expenses of firm $1$, firm $2$ has an additional incentive ???do you mean by ``additional'' that $dx_{1}/dx_{2} <0$?
+But in Nash equil.
+2 takes $x_1$ as given???
+to have higher efforts and firm $1$ to reduce its efforts.
 This fact does not depend on the market shares, so supporting the weak firm always reduces the efforts of the leader.
@@
 	\item Market shares determine investments. Are returns convex or concave?
-	\item Customers profit from investment. The large firm has more customers. If it invests more, it helps more people. 
+	\item Customers profit from investment. The large firm has more customers. If it invests more, it helps more people. ???socially optimal asymmetry???
 	\item What is the social optimum?
